---
title: "Find the best available evidence for a question in medicine"
output: html_document
---

Say you are interested in finding out the names of the safest NSAID painkillers. The following steps will get you a list of Cochran reviews. (Step 07 only works in Chrome, so start in Chrome.)

1.  Navigate to <https://www.cochranelibrary.com/>

2.  type "painkiller" and "side effects" in the search box

3.  Open the top hit

4.  Navigate to the section titled "Keywords (MeSH, PICOs)" using the scroll bar on the right

5.  Click the item with the desired qualifier: "Anti‐Inflammatory Agents, Non‐Steroidal [\*administration & dosage, adverse effects];"

6.  Click view results

7.  Export selected citations as a CSV file.

Then you can remove irrelevant reviews by data wrangling.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
citations <- read_csv("C:/Users/abhalla/Downloads/citation-export.csv")

keep <- citations |> pull(Title) |>  str_which("Single|Topical|Child|child", negate = TRUE)
```

Generate hyperlinked table as described [here](https://community.rstudio.com/t/create-interactive-links-in-gt-table-in-rmarkdown/70266/2).

```{r}
citations |> slice(keep) |> select(Title, URL) |> mutate(
        link = glue::glue("[website]({URL})"),
        link = map(link, gt::md)) |> 
  select(-URL) |> rownames_to_column() |> rename("#" = rowname) |> 
    gt::gt()
```
